\Title

### 2016-10-06 manuscript/manuscript.tex
Add reference to archived repo on figshare

All source code, Jupyter notebooks, data, and results
can be found at the online repository
\url{https://github.com/pinga-lab/paper-moho-inversion-tesseroids}.
The repository also contains instructions for replicating all results presented
here.
An archived version of this repository is also available at
\url{http://dx.doi.org/...}
(\textbf{Note to reviewers: the archived version will be uploaded upon
publication}).

>>>>

All source code, Jupyter notebooks, data, and model results
are made available through an online repository
\citep[][ \url{http://dx.doi.org/10.6084/m9.figshare.3987267} or
\url{https://github.com/pinga-lab/paper-moho-inversion-tesseroids}]{uieda2016a}.
The repository also contains instructions for replicating all results presented
here.
